The Unintended Consequences of Energy Reduction

### 2024-02-15 paper/paper.qmd
added a data + measurement section

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

>>>>

In an attempt to understand impact of the Fukushima disaster through data we looked at the changes over time of many variables. The first variable we examined was the number of ambulance calls for heatstroke. This data was collected from the Fire and Disaster Management Agency in Japan and was a good fit for our analysis as we wanted to really wanted to study the changes in heatstroke occurrences over time.

Additionally, we also considered health datasets which may have helped us analyze heatstroke occurrences directly, but they were all in Japanese and usually consisted of multiple other illnesses making these datasets difficult to parse through. We felt that this particular dataset could capture the relationship between heatstroke and time well.

Looking at ambulance calls was our way of measuring heatstroke occurrences. This way of measurement has the advantage of being concrete while trying to measure health symptoms can be challenging and subjective. A flaw with this way of measurement is that it misses people with heatstroke who didn’t call an ambulance.

The second variable we examined was the domestic energy production of Japan in terajoules. We collected this dataset from the International Energy Agency. This variable is easy to measure due to the high barrier of entry energy production at a large scale requires. Japan has 10 major energy companies that supply energy to the nation and any additional energy production wouldn’t go unnoticed.

Another variable we also considered was Japan’s mortality rate. We used the data from the National Institute of Population and Social Security Research of Japan in our analysis due to the reputability of the source. Mortality can be difficult to measure considering just how large human populations can be. Documenting all cases of mortality may not be possible, especially for people with few friends and family.

Lastly we studied energy consumption (MWH), and the price of 1MWH in yen. To study these variables we used data from the Federation of Electric Power Companies of Japan (FEPC). This is data directly from the source of Japan’s domestic energy, so we preferred it over other datasets. Measuring energy consumption is easy because it has a price tag attached to it. Since most transactions occur via the internet these days, it’s pretty easy to keep track of all price and consumption data. However, a human error of records could affect the measurements.
